The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-22 paper.tex
update

Fourth, the good agreement between the simulated and observed gamma-ray/microwave spectra\
imply that, in the presence of ISRF and magnetic fields, the emission of the Fermi bubbles and\
the microwave haze can be produced by the same high-energy electrons\
via inverse Compton scatterings and synchrotron radiations, respectively,\
as previously suggested \citep{Su2010,Dobler2012}.

>>>>

Fourth, the good agreement between the simulated and observed gamma-ray/microwave spectra\
implies that, in the presence of ISRF and magnetic fields, the emission of the Fermi bubbles and\
the microwave haze can be produced by the same high-energy electrons\
via inverse Compton scatterings and synchrotron radiations, respectively,\
as previously suggested \citep{Su2010,Dobler2012}.
